Under-approximation of reachability through static analysis in multivalued asynchronous networks

### 2013-03-31 parts/def-ph.tex
start cleanup

\noindent
The sort of a process $a_i$ is referred to as $\PHsort(a_i)=a$ and the set of sorts present in an action $h\in\PHa$ as $\PHsort(h) = \{\PHsort(\PHhitter(h)),\PHsort(\PHtarget(h))\}$.
Given a state $s\in \PHl$, the process of sort $a\in\PHs$ present in $s$ is denoted by $\PHget{s}{a}$, that is the $a$-coordinate of the state $s$.
If $a_i\in \PHl_a$, we define the notation $a_i\in s \EQDEF \PHget{s}{a}=a_i$.
We define the semantics of actions in a Process Hitting model in \pref{def:play}.

\begin{definition}
\label{def:play}
  An action $h = \PHhit{a_i}{b_j}{b_k} \in \PHa^{(n)}$ of priority $n$ is \emph{playable} in $s \in \PHl$ iff $\PHget{s}{a} = a_i$, $\PHget{s}{b} = b_j$ and $\forall m < n, \forall g \in \PHa^{(m)}, \PHhitter(g) \notin s \vee \PHtarget(g) \notin s$.
  In such a case, $(s \PHplay h)$ stands for the state resulting from the play of the action $h$ in $s$, defined by: $\PHget{(s \PHplay h)}{b} = b_k$ and $\forall c\in\PHs, c\neq b, \PHget{(s\PHplay h)}{c} = \PHget{s}{c}$.
  For the sake of clarity, for all $h, h'\in\PHa$, $((s\PHplay h)\PHplay h')$ is abbreviated as $(s\PHplay h\PHplay h')$.
\end{definition}

\begin{definition}[Scenario ($\Sce$)]
\label{def:scenario}
  For a given Process Hitting model $(\PHs,\PHl,\PHh)$,
  a \emph{scenario} $\delta$ is a sequence of actions of $\PHh$ so that for all $n \in \indexes{\delta}$,
  $a_i = \PHhitter(\delta_n)$ (resp. $\PHtarget(\delta_n)$) $\Rightarrow \last_a(\delta_{1..n-1}) \in \{ \varnothing, a_i \}$.
  The set of all scenarios is noted $\Sce$.
\end{definition}

\begin{definition}[Process Hitting $n$-reduction] \towrite{Revoir terminologie : “reduction” ? “restriction” ?}
  If $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$ is a Process Hitting with $k$ priorities and $n \in \segm{1}{k}$, we denote $\restriction{\PH}{n}$ \towrite{$\PH_{|n}$ $\PH'$} the $n$-reduction of $\PH$ the following Process Hitting with $n$ priorities:
  $\restriction{\PH}{n} = (\PHs; \PHl; \restriction{\PHa}{n})$,
  with:
  $$\restriction{\PHa}{n} = (\PHa^{(1)}; \dots; \PHa^{(n)})$$
  Furthermore, we denote: $\restriction{\Sce}{n}$ the set of scenarios of actions of $\restriction{\PHa}{n}$.
\end{definition}

@@

\paragraph{2 priorities}
In this paper, we only consider Process Hitting models with 2 priorities.

This restriction allows to models two kinds of actions: controllable actions that model the non-determinacy of biological evolutions,
and uncontrollable actions that are used to model non-biological behaviours in the model.

In \pref{def:component} we define the notion of well-formed component.
A sort $a$ is a well-formed component iff
it is hit only by actions of priority $2$.
\begin{definition}
\label{def:component}
  A sort $a \in \PHs$ is said to be a well-formed component iff:
  \begin{itemize}
    \item $\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) = 2$
  \end{itemize}
\end{definition}
We call $\components$ the set of well-formed components.

\begin{definition}
\label{def:chainsactions}
  We define the set of chains of actions $\PHh(b, a)$ between two sorts $b$ and $a$ as below:
  \begin{align*}
  \PHh(b, a) = \{ (h_i)_{i \in \segm{0}{s}} \in (\PHh^{(1)})^{s+1} &\mid s \in \sN, \PHsort(\PHhitter(h_0)) = b \wedge \PHsort(\PHtarget(h_s)) = a \\
    & \wedge \forall i \in \segm{1}{s}, \PHsort(\PHtarget(h_{i-1})) = \PHsort(\PHhitter(h_{i})) \}
  \end{align*}
\end{definition}

\paragraph{Cycle-freeness between actions of priority $1$}
There is no cycle in chains of actions: $\forall a \in \PHs, \PHh(a, a) = \emptyset$.

Given this first hypothesis, we define the neighbor \towrite{revoir terminologie : neighbors ? vicinity ?} sorts and actions (\pref{def:neighbors}).
\begin{definition}
\label{def:neighbors}
  The set of neighbour sorts $\Vs(a)$ of a given sort $a$ is the set of components that can interact with it through actions of priority $1$.
  The set of neighbour actions $\Vh(a)$ of $a$ is the set of actions of priority $1$ influencing $a$.
  $$\Vs(a) = \{ b \in \components \mid \PHh(b, a) \neq \emptyset \}$$
  $$\Vh(a) = \{ h \in \PHh^{(1)} \mid \PHsort(\PHhitter(h)) \in \Vs(a) \wedge \PHsort(\PHtarget(h)) \in \Vs(a) \cup \{ a \} \}$$
\end{definition}

We denote $\pfp_s(a)$ the set of possible local steady-states of a sort $a$ from a state $s$.
\todo{À corriger : état global ?}
\begin{align*}
  \pfp_s(a) = \{ a_i \in \PHl_a &\mid \exists \delta \in \restriction{\Sce}{1}, \PHget{(s \PHplay \delta)}{a} = a_i \\
  & \quad \wedge \forall \PHhit{b_i}{c_j}{c_k} \in \Vh(a), \PHget{(s \PHplay \delta)}{b} \neq b_i \vee \PHget{(s \PHplay \delta)}{c} \neq c_j \}
\end{align*}
Of course, if $a \in \components$, then $\pfp_s(a) = \PHget{s}{a}$.

In \pref{def:cs} we define the notion of well-formed cooperative sort.
A cooperative sort $a$ is well-formed iff
it is hit only by actions of priority $1$,
any sub-state of its neighbourhood is represented by exactly one local steady state in this sort,
and all of its processes represents at least one sub-state of its neighbourhood.
\begin{definition}
\label{def:cs}
  A sort $a \in \PHs$ is said to be a well-formed cooperative sort iff:
  \begin{itemize}
    \item $\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) = 1$
    \item $\forall s \in \underset{b \in \Vs(a)}{\times} \PHl_b, |\pfp_s(a)| = 1$
    \item $\forall a_i \in \PHl_a, \exists s \in \underset{b \in \Vs(a)}{\times} \PHl_b, \pfp_s(a) = \{ a_i \}$
  \end{itemize}
\end{definition}
We call $\cs$ the set of well-formed cooperative sorts.
%We note that: $\forall a \in \components, \Vs(a) = \emptyset \wedge \Vh(a) = \emptyset$
As any local state of neighbour sorts of a cooperative sort leads to a local steady-state, we denote $\csState(a_i)$ the set of sub-states represented by the process $a_i$ of the cooperative sort $a$.
\begin{definition}[$\csState$]
\label{def:csState}
  \towrite{À reformuler}
  $$\csState(a_i) = \{ s \in \underset{b \in \Vs(a)}{\times} \PHl_b \mid \pfp_{s}(a) = a_i \}$$
\end{definition}

\paragraph{Components \& cooperative sorts}
The studied PH is a PH with 2 priorities, and it is only composed of well-formed components and cooperative sorts:
$\components \cup \cs = \PHs \wedge \components \cap \cs = \emptyset$

\paragraph{Bounded termination}
The dynamics of model $\restriction{\PH}{1}$ contains no cycles. Cycles are still allowed in $\PH$ however.
Formally : $\exists N \in \sN, \forall \delta \in \restriction{\Sce}{1}, |\indexes{\delta}| \leq N$.

\subsection{Consequences of the restrictions}
Given these hypotheses, we can denote: $\pfp_s(a) = a_i$ the local steady-state of $a$ in state $s$.
Furthermore, we denote by $\update(s)$ the state in which all cooperative sorts are updated.
\begin{align*}
  \update(s) = s \underset{a \in CS}{\Cap } \pfp_{s}(a)
\end{align*}
where for all process $a_i$, $s \Cap a_i$ is the state defined by:
$\PHget{(s \Cap a_i)}{a} = a_i \wedge \forall b \neq a, \PHget{(s \Cap a_i)}{b} = \PHget{s}{b}$.

\pref{th:update} states that from any state, there exists a scenario updating the cooperative sorts of this state.
\begin{theorem}
\label{th:update}
  $\forall s \in \PHl, \exists \delta \in \restriction{\Sce}{1}, s \PHplay \delta = \update(s)$
\end{theorem}
\begin{proof}
  Let $a$ be a cooperative sort so that $\PHget{s}{a} \neq \pfp_s(a)$.
  Given the definition of $\pfp_s(a)$, there exists a scenario updating $a$ in $s$.
  As there is no cycle in between the cooperative sorts and an updated cooperative sort cannot evolve, at most $|\cs|$ updates can be done.
\end{proof}
\pref{th:hcompcomp} states that for a given state $s$ and for any action $h = \PHhit{a_i}{b_j}{b_k}$ between well-formed components, $h$ can be played after a series of hits that do not prevent it to be fired.
\pref{th:hcscomp} states the same if $a$ is a well-formed cooperative sort, under the condition that $a_i$ reflects the state of the neighborhood of $a$.
\begin{theorem}
\label{th:hcompcomp}
  $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, a,b \in \components,$\\
  $(\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j) \Rightarrow (\exists \delta \in \restriction{\Sce}{1}, \text{$h$ can be played in $s \PHplay \delta$})$
\end{theorem}
\begin{proof}
  From \pref{th:update}, there exists a scenario $\delta$ so that: $(s \PHplay \delta) = \update(s)$.
  As $a,b \in \components$, $a_i \in s \PHplay \delta$ and $b_j \in s \PHplay \delta$.
  Finally, by definition of $\update(s)$, no action of priority $1$ can be played in $s \PHplay \delta$, thus $h$ can be played in $s \PHplay \delta$.
\end{proof}
\begin{theorem}
\label{th:hcscomp}
  $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, a \in \cs, b \in \components$\\
  $(\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j \wedge \pfp_s(a) = a_i) \Rightarrow (\exists \delta \in \restriction{\Sce}{1}, \text{$h$ can be played in $s \PHplay \delta$})$
\end{theorem}
\begin{proof}
  From \pref{th:update}, there exists a scenario $\delta$ so that: $(s \PHplay \delta) = \update(s)$.
  As $a_i \in \pfp_s(a)$, $a_i \in s \PHplay \delta$.
  Furthermore, $b \in \components$, thus $b_j \in s \PHplay \delta$.
  Finally, by definition of $\update(s)$, no action of priority $1$ can be played in $s \PHplay \delta$, thus $h$ can be played in $s \PHplay \delta$.
\end{proof}

\pref{th:autohits} states that any sequence $\zeta$ of self-actions on a well-formed component can be played eventually.
\begin{theorem}
\label{th:autohits}
  Let $a \in \PHs$, $s \in \PHl$ and $\zeta \in \BS$ so that $\forall i \in \indexes{\zeta}, \PHsort(\PHhitter(\zeta_i)) = \PHsort(\PHtarget(\zeta_i)) = a$.
  $\exists (\delta_i)_{i \in \indexes{\zeta}} \in \restriction{\Sce}{1}$ so that $\forall i \in \indexes{\zeta}$, $\zeta_i$ can be played in $s \PHplay \delta_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_i$. 
\end{theorem}
\begin{proof}
  With \pref{th:hcompcomp} applied iteratively.
\end{proof}

>>>>

\noindent
The sort of a process $a_i$ is referred to as $\PHsort(a_i) = a$.
%and the set of sorts present in an action $h \in \PHa$ as $\PHsort(h) = \{\PHsort(\PHhitter(h)),\PHsort(\PHtarget(h))\}$.
Given a state $s\in \PHl$, the process of sort $a \in \PHs$ present in $s$ is denoted by $\PHget{s}{a}$, that is the $a$-coordinate of the state $s$.
If $a_i \in \PHl_a$, we define the notation $a_i \in s \EQDEF \PHget{s}{a} = a_i$.
We define the override of a state by a process in \pref{def:statecap}, which allows to define the dynamics in a Process Hitting model (\pref{def:play}).
\begin{definition}
\label{def:statecap}
  Given a state $s \in \PHl$ and a process $a_i \in \PHproc$, $(s \Cap a_i)$ is the state defined by:
  $\PHget{(s \Cap a_i)}{a} = a_i \wedge \forall b \neq a, \PHget{(s \Cap a_i)}{b} = \PHget{s}{b}$.
  We also extend this definition to a set of processes $ps$ given that all processes are from different sorts by the override of each process:
  $\forall as \subset \PHs, \forall ps \in \underset{a \in as}{\times} \PHl_a, s \Cap ps = s \underset{a_i \in ps}{\Cap} a_i$.
\end{definition}
\begin{definition}
\label{def:play}
  An action $h = \PHhit{a_i}{b_j}{b_k} \in \PHa^{(n)}$ of priority $n$ is \emph{playable} in $s \in \PHl$
  if and only if $\PHget{s}{a} = a_i$, $\PHget{s}{b} = b_j$ and $\forall m < n, \forall g \in \PHa^{(m)}, \PHhitter(g) \notin s \vee \PHtarget(g) \notin s$.
  In such a case, $(s \PHplay h)$ stands for the state resulting from the play of the action $h$ in $s$, defined by: $(s \PHplay h) = s \Cap \PHbounce(h)$.
%  For the sake of clarity, for all $h, h'\in\PHa$, $((s\PHplay h)\PHplay h')$ is abbreviated as $(s\PHplay h\PHplay h')$.
\end{definition}
%\begin{definition}[Scenario ($\Sce$)]
%\label{def:scenario}
  For a given state $s \in \PHl$,
  a \emph{scenario} $\delta$ from $s$ is a sequence of actions of $\PHh$ that can be played successively in $s$.
%  so that for all $n \in \indexes{\delta}$,
%  $a_i = \PHhitter(\delta_n)$ (resp. $\PHtarget(\delta_n)$) $\Rightarrow \last_a(\delta_{1..n-1}) \in \{ \varnothing, a_i \}$.
  The set of all scenarios from $s$ is noted $\Sce(s)$.
%\end{definition}

\begin{definition}[Process Hitting $n$-reduction] \towrite{Revoir terminologie : “reduction” ? “restriction” ?}
  If $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$ is a Process Hitting with $k$ priorities and $n \in \segm{1}{k}$, we denote $\restriction{\PH}{n}$ \towrite{$\PH_{|n}$ $\PH'$} the $n$-reduction of $\PH$ the following Process Hitting with $n$ priorities:
  $\restriction{\PH}{n} = (\PHs; \PHl; \restriction{\PHa}{n})$,
  with:
  $$\restriction{\PHa}{n} = (\PHa^{(1)}; \dots; \PHa^{(n)})$$
  Furthermore, we denote: $\restriction{\Sce}{n}(s)$ the set of scenarios from $s$ made of actions of $\restriction{\PHa}{n}$.
\end{definition}

@@

\begin{criterion}[2 priorities]
\label{cr:2prio}
%\paragraph{2 priorities}
  In this paper, we only consider Process Hitting models with 2 priorities.
\end{criterion}

\pref{cr:2prio} allows to models two kinds of actions: controllable actions that model the non-determinacy of biological evolutions,
and uncontrollable actions that are used to model non-biological behaviours in the model.

In \pref{def:component} we define a well-formed component as a sort that is hit only by actions of priority $2$.
\begin{definition}
\label{def:component}
  A sort $a \in \PHs$ is said to be a well-formed component if and only if:
  $$\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) = 2 \enspace.$$
  We call $\components$ the set of well-formed components.
\end{definition}

\begin{definition}
\label{def:chainsactions}
  The set of chains of actions $\PHh(b, a)$ between two sorts $b$ and $a$ is defined as below:
  \begin{align*}
  \PHh(b, a) = \{ (h_i)_{i \in \segm{0}{s}} \in (\PHh^{(1)})^{s+1} &\mid s \in \sN, \PHsort(\PHhitter(h_0)) = b \wedge \PHsort(\PHtarget(h_s)) = a \\
    & \wedge \forall i \in \segm{1}{s}, \PHsort(\PHtarget(h_{i-1})) = \PHsort(\PHhitter(h_{i})) \}
  \end{align*}
\end{definition}

\begin{criterion}[Cycle-freeness between actions of priority $1$]
\label{cr:cyclefreeness}
%\paragraph{Cycle-freeness between actions of priority $1$}
  There is no cycle in chains of actions:
  $$\forall a \in \PHs, \PHh(a, a) = \emptyset \enspace.$$
\end{criterion}

Given \pref{cr:cyclefreeness}, we define the neighbour \towrite{revoir terminologie : neighbors ? vicinity ?} sorts and actions (\pref{def:neighbors}).
\begin{definition}[Neighbour sorts ($\Vs$) and Neighbour actions ($\Vh$)]
\label{def:neighbors}
  The set of neighbour sorts $\Vs(a)$ of a given sort $a$ is the set of components that can interact with it through actions of priority $1$.
  The set of neighbour actions $\Vh(a)$ of $a$ is the set of actions of priority $1$ influencing $a$.
  $$\Vs(a) = \{ b \in \components \mid \PHh(b, a) \neq \emptyset \}$$
%  $$\Vh(a) = \{ h \in \PHh^{(1)} \mid \PHsort(\PHhitter(h)) \in \Vs(a) \wedge \PHsort(\PHtarget(h)) \in \Vs(a) \cup \{ a \} \}$$
  $$\Vh(a) = \{ h \in \PHh^{(1)} \mid \exists b \in \Vs(a), \exists hs \in \PHh(b,a), h \in hs \}$$
\end{definition}

We denote $\pfp_s(a)$ the set of processes of sort $a$ that can be reached from state $s$ and that are local steady-states.
%the set of possible local steady-states of a sort $a$ from a state $s$.
%\todo{À corriger : état global ?}
\begin{definition}[Local steady-state ($\pfp$)]
\label{def:pfp}
  For all $a \in \PHa$ and $s \in \PHl$,
  \begin{align*}
    \pfp_s(a) = \{ a_i \in \PHl_a &\mid \exists \delta \in \restriction{\Sce}{1}(s), \PHget{(s \PHplay \delta)}{a} = a_i \\
    & \quad \wedge \forall \PHhit{b_i}{c_j}{c_k} \in \Vh(a), \PHget{(s \PHplay \delta)}{b} \neq b_i \vee \PHget{(s \PHplay \delta)}{c} \neq c_j \}
  \end{align*}
  Of course, if $a \in \components$, then $\pfp_s(a) = \{ \PHget{s}{a} \}$.
\end{definition}

In \pref{def:cs} we define a well-formed cooperative sort as a sort that is only by actions of priority $1$ and so that
any sub-state of its neighbourhood is represented by exactly one local steady state in this sort,
and all of its processes represents at least one sub-state of its neighbourhood. \towrite{reformuler ou supprimer}
\begin{definition}
\label{def:cs}
  A sort $a \in \PHs$ is said to be a well-formed cooperative sort iff:
  \begin{enumerate}
    \item $\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) = 1$
%    \item $\forall s \in \underset{b \in \Vs(a)}{\times} \PHl_b, |\pfp_s(a)| = 1$
%    \item $\forall a_i \in \PHl_a, \exists s \in \underset{b \in \Vs(a)}{\times} \PHl_b, \pfp_s(a) = \{ a_i \}$
    \item \label{csai} $\forall s \in \PHl, |\pfp_s(a)| = 1$
    \item \label{css} $\forall a_i \in \PHl_a, \exists s \in \PHl, \pfp_s(a) = \{ a_i \}$
  \end{enumerate}
\end{definition}
We call $\cs$ the set of well-formed cooperative sorts.
%We note that: $\forall a \in \components, \Vs(a) = \emptyset \wedge \Vh(a) = \emptyset$
Because of (\ref{csai}), we denote in the following: $\pfp_s(a) = a_i$.
Furthermore, because of (\ref{css}), we denote $\csState(a_i)$ the set of sub-states represented by the process $a_i$ of the cooperative sort $a$ (\pref{def:csState}).
\begin{definition}[Represented sub-states ($\csState$)]
\label{def:csState}
  $$\csState(a_i) = \{ ps \in \underset{b \in \Vs(a)}{\times} \PHl_b \mid \forall s \in \PHl, \pfp_{s \Cap ps}(a) = a_i \}$$
\end{definition}

\begin{criterion}[Components \& cooperative sorts]
\label{cr:compcs}
%\paragraph{Components \& cooperative sorts}
  The studied PH is a PH with 2 priorities, and it is only composed of well-formed components and cooperative sorts:
  $$\components \cup \cs = \PHs \wedge \components \cap \cs = \emptyset \enspace.$$
\end{criterion}

\begin{criterion}[Bounded termination]
\label{cr:bounded}
%\paragraph{Bounded termination}
  The dynamics of model $\restriction{\PH}{1}$ contains no cycles:
  %Cycles are still allowed in $\PH$ however.
  %Formally :
  $$\exists N \in \sN, \forall \delta \in \restriction{\Sce}{1}, |\indexes{\delta}| \leq N \enspace.$$
\end{criterion}

\subsection{Consequences of the restrictions}
%Given these hypotheses, we can denote: $\pfp_s(a) = a_i$ the local steady-state of $a$ in state $s$.
We denote by $\update(s)$ the state in which all cooperative sorts are updated.
\begin{align*}
  \update(s) = s \Cap \{ \pfp_{s}(a) \mid a \in CS \} \enspace.
\end{align*}

\pref{th:update} states that from any state, there exists a scenario updating the cooperative sorts of this state.
\begin{theorem}
\label{th:update}
  $\forall s \in \PHl, \exists \delta \in \restriction{\Sce}{1}(s), s \PHplay \delta = \update(s)$
\end{theorem}
\begin{proof}
  Let $a$ be a cooperative sort so that $\PHget{s}{a} \neq \pfp_s(a)$.
  Given the definition of $\pfp_s(a)$, there exists a scenario updating $a$ in $s$.
  As there is no cycle in between the cooperative sorts and an updated cooperative sort cannot evolve, at most $|\cs|$ updates can be done.
\end{proof}
\pref{th:hcompcomp} states that for a given state $s$ and for any action $h = \PHhit{a_i}{b_j}{b_k}$ between well-formed components, $h$ can be played after a series of hits that do not prevent it to be fired.
\pref{th:hcscomp} states the same if $a$ is a well-formed cooperative sort, under the condition that $a_i$ reflects the state of the neighborhood of $a$.
\begin{theorem}
\label{th:hcompcomp}
  $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, a,b \in \components,$\\
  $(\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j) \Rightarrow (\exists \delta \in \restriction{\Sce}{1}(s), \text{$h$ can be played in $s \PHplay \delta$})$
\end{theorem}
\begin{proof}
  From \pref{th:update}, there exists a scenario $\delta$ so that: $(s \PHplay \delta) = \update(s)$.
  As $a,b \in \components$, $a_i \in s \PHplay \delta$ and $b_j \in s \PHplay \delta$.
  Finally, by definition of $\update(s)$, no action of priority $1$ can be played in $s \PHplay \delta$, thus $h$ can be played in $s \PHplay \delta$.
\end{proof}
\begin{theorem}
\label{th:hcscomp}
  $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, a \in \cs, b \in \components$\\
  $(\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j \wedge \pfp_s(a) = a_i) \Rightarrow (\exists \delta \in \restriction{\Sce}{1}(s), \text{$h$ can be played in $s \PHplay \delta$})$
\end{theorem}
\begin{proof}
  From \pref{th:update}, there exists a scenario $\delta$ so that: $(s \PHplay \delta) = \update(s)$.
  As $a_i \in \pfp_s(a)$, $a_i \in s \PHplay \delta$.
  Furthermore, $b \in \components$, thus $b_j \in s \PHplay \delta$.
  Finally, by definition of $\update(s)$, no action of priority $1$ can be played in $s \PHplay \delta$, thus $h$ can be played in $s \PHplay \delta$.
\end{proof}

\begin{comment}
\pref{th:autohits} states that any sequence $\zeta$ of self-actions on a well-formed component can be played eventually.
\begin{theorem}
\label{th:autohits}
  Let $a \in \PHs$, $s \in \PHl$ and $\zeta \in \BS$ so that $\forall i \in \indexes{\zeta}, \PHsort(\PHhitter(\zeta_i)) = \PHsort(\PHtarget(\zeta_i)) = a$.
  $\exists (\delta_i)_{i \in \indexes{\zeta}} \in \restriction{\Sce}{1}$ so that $\forall i \in \indexes{\zeta}$, $\zeta_i$ can be played in $s \PHplay \delta_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_i$. 
\end{theorem}
\begin{proof}
  With \pref{th:hcompcomp} applied iteratively.
\end{proof}
\end{comment}
